\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-12-02 paper.qmd
Added initial projection layouts

>>>>

```{r}
#| label: pbmc-umap-model-proj-scdeed

## First projection
projection <- cbind(
  c(0.040856,0.000723,0.006000,0.007623,0.001986,-0.006599,0.005311,-0.000222,0.001648,0.008067,-0.001587,0.004423,0.004851,0.000638,0.002606,0.006616,0.006188,-0.000954,-0.004603,0.004998,-0.012220,0.008401,-0.007788,0.008972,-0.003903,0.003348,-0.001817,-0.000385,-0.002437,-0.004097,-0.001357,0.013660,0.001770,0.006982,0.002828,-0.009169,-0.003541,0.008582,-0.000032,-0.002375,0.005854,-0.005466,-0.000824,-0.001435,0.004148,0.007141,0.000883,-0.004159,0.005401,0.007882),
  c(-0.000590,0.039365,-0.004481,-0.009041,-0.003805,0.003278,-0.009601,-0.000650,-0.002333,-0.005697,-0.001488,-0.009808,0.002557,0.004113,0.005705,-0.004665,-0.001170,-0.004727,-0.000845,0.005084,-0.018054,0.002538,0.006606,-0.007184,0.000238,0.001877,-0.002124,-0.005972,-0.009729,0.004958,-0.003181,-0.005185,-0.009598,-0.004243,0.007716,0.000396,-0.004258,0.005932,-0.003242,-0.004184,0.003493,-0.008405,0.000860,0.008304,0.004569,0.000798,0.004156,-0.005777,0.005278,-0.002531))

## Second projection
projection <- cbind(
  c(-0.019825,-0.011101,0.011543,-0.006943,-0.004485,0.000062,0.002023,-0.005178,0.000800,-0.002903,-0.014182,0.008756,0.009595,0.007032,-0.007820,0.006143,0.004865,0.003352,0.007554,0.002265,0.012035,0.009961,-0.001825,-0.004942,-0.002237,0.002308,0.009531,-0.001146,0.013401,-0.001022,0.008434,0.000477,0.004239,-0.006772,-0.004702,-0.011432,-0.000431,0.008146,-0.009299,-0.004782,0.003457,-0.008214,-0.009604,0.011329,0.003805,-0.003004,-0.000800,0.015288,-0.013157,0.006984),
  c(-0.001387,0.001643,0.010470,0.002930,-0.002335,-0.010569,0.013839,0.002917,-0.006825,0.010191,-0.006367,0.002220,0.002506,0.005139,-0.007213,-0.006235,-0.007123,-0.000222,-0.002225,0.011592,-0.003942,0.002788,-0.000055,0.011316,-0.009753,0.020785,0.004615,0.005172,0.011182,-0.003125,-0.010860,0.007820,-0.017510,0.007010,0.007267,0.002694,-0.003949,-0.009188,-0.005163,0.001898,-0.004744,0.013757,0.010630,-0.007688,0.004598,0.004658,-0.011154,0.003584,-0.005226,0.006650))

pbmc_proj_umap_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1,
      y = proj2)) +
  geom_segment(
    data = model_df,
    aes(
      x = proj1_from,
      y = proj2_from,
      xend = proj1_to,
      yend = proj2_to),
    color = "#000000") +
  geom_point(
    #size = 0.5,
    alpha = 0.2,
    color = '#a65628') +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2),
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle,
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-1, 0.75)) +
  ylim(c(-1, 0.75)) +
  interior_annotation("a3", cex = 2)
```

```{r}
#| echo: false
#| fig-cap: "Model in \\gD{}, on the layout a, and two views of the fit in projections from $50\\text{-}D$, for the PBMC3k data ($n =  5858$ and $p = 50$). Layout shows close clusters. In $50\\text{-}D$, the data shows "
#| label: fig-model-pbmc-author-proj-scdeed
#| fig-pos: H
#| fig-width: 10
#| fig-height: 15
#| out-height: 80%

free(trimesh_removed_pbmc) + 
  pbmc_proj_umap_model1 + 
  pbmc_proj_umap_model2 + 
  plot_layout(nrow=3) &
  theme(legend.position='none')
```

### 2024-12-02 paper.tex
Added initial projection layouts

>>>>

\includegraphics[width=1\textwidth,height=0.8\textheight]{paper_files/figure-pdf/fig-model-pbmc-author-proj-scdeed-1.pdf}

\caption{\label{fig-model-pbmc-author-proj-scdeed}Model in \gD{}, on the
layout a, and two views of the fit in projections from \(50\text{-}D\),
for the PBMC3k data (\(n =  5858\) and \(p = 50\)). Layout shows close
clusters. In \(50\text{-}D\), the data shows}
